Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-17 paper/v2/paper-edited.tex
minor changes to abstract; cleaner title header

\author{%
Ryan Beckett\\
  \affaddr{Princeton University}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft Research}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitu Padhye\\
  \affaddr{Microsoft Research}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton University}
  %\\
  %\email{dpw@princeton.edu}
}

@@

\textbf{Abstract---}
We develop \sysname, a language and a compiler to help network operators with a challenging, error-prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
%
The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
%through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
%It uses We introduce data structures and algorithms that
It guarantees that the compiled configurations correctly implement the specified policy under all possible combinations of failures.
%
We use \sysname for datacenter and backbone networks of a large cloud provider. We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.

>>>>

\author{%
Ryan Beckett\\
  \affaddr{Princeton}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{UCLA}
  %\affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and 
Jitu Padhye\\
  \affaddr{Microsoft}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton}
  %\\
  %\email{dpw@princeton.edu}
}

@@

\textbf{Abstract---}
We develop \sysname, a language and compiler to help network operators with a challenging, error-prone task---bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
%
The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
%through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
%It uses We introduce data structures and algorithms that
It guarantees that the compiled configurations correctly implement the specified policy under all possible combinations of failures.
%
We show that \sysname can effectively express the policies of datacenter and backbone networks of a large cloud provider;  and despite its strong guarantees, our compiler scales to networks with hundreds or thousands of routers.
